---
title: "Homework 4"
output:
  pdf_document: default
  html_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
  
  
**1.(3 points) Use the rvest R package to scrape the schedule and materials table into R from the course webpage (https://introdatasci.dlilab.com/schedule_materials/). Read the documentation of rvest so you get a better idea about the functions provided by rvest and their usages.**  
  

```{r}
library(rvest)
webpage_data <- read_html("https://introdatasci.dlilab.com/schedule_materials/")
table <- webpage_data %>%
  html_nodes(xpath='//*[@id="main"]/table') %>%
  html_table()
table <- table[[1]]
print(table)

```
  
  
**2. (2 points) With the extracted data frame, create two new columns based on the Date column: month and day. month would be the month abbrevations from the Date column; day would be the numeric numbers from the Date column. Although you can use whatever approach to get this done (do not enter them by hand…), I suggest you try to practice regular expression here (sub() or stringr::str_extract()).**  


```{r}
library(stringr)
month <- str_extract(table$Date, boundary("word"))
day <- str_extract(table$Date, "\\d?\\d")
table <- data.frame(table, month, day)
table
```
  
  
**3. (2 points) With the data frame generated from Q2, use group_by() and summarise() to find out the number of lectures for each month, order the results by the number of lectures (high to low).**  
  
  
```{r}
library(dplyr)
table %>%
	group_by(month) %>%
	summarise(lecture_count = n())%>%
	arrange(desc(lecture_count))
```
  
  
  
**4. (3 points) For the Topic column, split all values into words (hint: stringr::str_split()). Observe the values in the Topic column and use regular expression to specify the pattern in the stringr::str_split() or strsplit() function. Once this is done, you should get a list of list, you can use unlist() to convert it into a vector and name it as words. Use table() and sort() to find the top 5 most frequent words.**  
  

```{r}
topic_words <- unlist(str_split(table$Topic, boundary("word")))
word_occurance <- sort(table(topic_words), decreasing = TRUE)
head(word_occurance, 5)
```

