---
title: "hw_02"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Question 1*

```{r}
mtcars[mtcars$cyl < 6,]
mtcars[-1:0, 1:3]
mtcars[mtcars$cyl == 8, ]
mtcars[mtcars$cyl ==  c(4,6), ]
```

*Question 2*

```{r}
x = (1:5)
print(x)
```
There should be parentheses around the (1:5) so NA isn't generated

*Question 3*
The R syntax is (row, columns), so you need to include the columns in the function mtcars(1:15, )

*Question 4*
```{r}
x = matrix(c(1:3, NA, 5:7, NA, NA), nrow = 3)
x[is.na(x)] = 0
print(x)
```
The first line of the code creates a matrix where 3 of the values are NA. The second line of code sets each of the NA values to 0, so when the matrix is printed each spot where an NA was returns a 0 instead.

```{r}
data("mtcars") ##get data
?mtcars
mpg2 <- 
ifelse(mtcars$mpg < 16, "low", 
ifelse(mtcars$mpg < 21, "low_intermediate",
ifelse(mtcars$mpg < 26, "intermediate_high", "high")))
##if less than 16, make mpg2 "low", if less than 21 but greater than 16, "low intermediate," if between 21 and 26, "intermediate high," everything above 26 is "high"
mtcars <- data.frame(mtcars, mpg2) ### merge the mpg2 data with the mtcars data set
head(mtcars)
```

